Automated topic naming to support analysis of software maintenance activities

### 2010-08-21 icse/icse2011.tex
more edits...
heh 10 pages
more abstract

Researchers have used topic modeling and concept location to understand the latent topics of software development artifacts.
These techniques use unsupervised machine-learning algorithms to recover topics.
These topics are word-lists and are difficult to distinguish and interpret. 
Topics are not meaningful until they have been named or interpreted.
Current topic labelling approaches are manual, and do not use domain-specific knowledge to improve, contextualize, or describe results for the developers.
We propose a solution: \emph{labelled topic extraction}.
Topics are extracted using Latent Dirichlet Allocation (LDA) from commit-log comments extracted from source control systems such as CVS and BitKeeper. 
These topics are given labels relating to a generalizable cross-project taxonomy consisting of non-functional requirements.
Our approach was evaluated  with experiments and case studies on two large-scale RDBMS projects: MySQl and MaxDB.
Labelled topic extraction produces appropriate, context-sensitive labels relevant to these projects, which provides fresh insight into their evolving software development activities.

@@

\textbf{Do label frequencies change over time?} -- In both projects the frequencies generally decreased with age. 
However, there are variations within our NFR labels. In MySQL, \emph{usability} and \emph{efficiency} do not appear very often in topics. 
A proportionately smaller number of commits addressed these NFRs.
As discussed in the previous section, certain peaks in topic numbers coincide with a particular emphasis from the development team on issues such as new releases or bug fixes.
This suggests that maintenance activity is not necessarily strictly decreasing with time, but rather episodic and responsive to outside stimuli. 
In MaxDB, we can observe that \emph{Maintainability} topics became more prevalent as MaxDB matures. 
This is likely due to our analysis time horizon being shorter than equivalent span for the MySQL product.

@@

%XXXXXXXX Optional  
\subsection{Future Work}

>>>>

Researchers have used topic modeling and concept location to understand the latent topics of software development artifacts.
These techniques use unsupervised machine-learning algorithms to recover topics.
These topics are word-lists and are difficult to distinguish and interpret. 
Topics are not meaningful until they have been named or interpreted.
Current topic labelling approaches are manual, and do not use domain-specific knowledge to improve, contextualize, or describe results for the developers.
We propose a solution: \emph{labelled topic extraction}.
Topics are extracted using Latent Dirichlet Allocation (LDA) from commit-log comments recovered from source control systems such as CVS and BitKeeper. 
These topics are given labels relating to a generalizable cross-project taxonomy consisting of non-functional requirements.
Our approach was evaluated  with experiments and case studies on two large-scale RDBMS projects: MySQl and MaxDB.
Labelled topic extraction produces appropriate, context-sensitive labels relevant to these projects, which provides fresh insight into their evolving software development activities.

@@

\textbf{Do label frequencies change over time?} -- In both projects the frequencies generally decreased with age. 
However, there are variations within our NFR labels. In MySQL, \emph{usability} and \emph{efficiency} do not appear very often in topics. 
A proportionately smaller number of commits addressed these NFRs.
As discussed in the previous section, certain peaks in topic numbers coincide with a particular emphasis from the development team on issues such as new releases or bug fixes.
This suggests that maintenance activity is not necessarily strictly decreasing with time, but rather episodic and responsive to outside stimuli. 
In MaxDB, we can observe that \emph{Maintainability} topics became more prevalent as MaxDB matures. 
This is likely due to our analysis time horizon being shorter than an equivalent span for the MySQL product. %XXXXXXXXXXXXXXXXX what

@@

%XXXXXXXX Optional  
%\subsection{Future Work}
